\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip

### 2015-03-04 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
update
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64797 15284696-431f-4ddb-bdfa-cd5b030d7da7

\title{\bigskip GRASS GIS: a peer-reviewed scientific platform and future research repository\bigskip}
\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$,Soeren Gebbert$^5$, Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, $^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Itlay}

@@

\begin{minipage}{0.25\textwidth}
\small {\url{www.bbk.ac.uk}}
\end{minipage}

>>>>

\title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, \\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, $^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Itlay}

@@

\begin{minipage}{0.25\textwidth}
\small {\url{grasswiki.osgeo.org}}
\end{minipage}
